Paper 1 Analysis

### 2016-07-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Better comment. Deleted unneeded code.
"" --> NULL for xlab.

resampleCoeffsCESFilename <- "EcolEcon2015kleResampleCoeffsCES.rds"
resampleModelsCESFilename <- "EcolEcon2015kleResampleModelsCES.rds"
ReModelsFilename <- "ReModels.rds"
if (rerunResampling){
  # Run some resampling on the PT and UK models that reject the cost-share theorem,
  # include energy, use quality-adjusted variables, and employ the (kl)e nesting.
  # This is u-g-l-y code. Just getting something running for now.
  modPT <- models$PT$adjusted$withE$CES$kle
  modUK <- models$UK$adjusted$withE$CES$kle
  resamplesCESPT <- resampledFits(modPT, method = "wild", n = nResamples)
  resamplesCESUK <- resampledFits(modUK, method = "wild", n = nResamples)
  # Resample model objects
  resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
  # Save this object in case we need to interrogate it later.
  # Note, however, that resampleModelsCES is NOT in the repository,
  # because it can be a HUGE file when we're doing, say, 1000 resamples.
  saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
  # Resample time series
  ReModels <-
    bind_rows(
      leaf_apply(resampleModelsCES, 
                 function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
                 strict.lists = TRUE)
    )
  saveRDS(ReModels, file = ReModelsFilename)
  # Resample coefficients
  resampleCoeffsCES <- bind_rows(
    bind_cols(resamplesCESPT$coeffs %>% mutate(Country="PT")), 
    bind_cols(resamplesCESUK$coeffs %>% mutate(Country="UK")))
  resampleCoeffsCES$energy <- TRUE
  resampleCoeffsCES$nest <- "(kl)e"
  saveRDS(resampleCoeffsCES, file = resampleCoeffsCESFilename)
} else {
  resampleCoeffsCES <- readRDS(resampleCoeffsCESFilename)
  # We don't need to load resampelModelsCES, because we use only ReModels later.
  # resampleModelsCES <- readRDS(resampleModelsCESFilename)
  ReModels <- readRDS(ReModelsFilename)
}
@

% <<ReModels>>=
% # ReModels is the data frame that holds time series of all the resample models.
% # We save this to disk and include it in the repo, because it is much smaller than resampleModelsCES.
% if (! rerunResampling){
%   ReModels <- readRDS(ReModelsFilename)
% } else {
%   # This code is expensive, so run only if we re-ran the resampling.
%   ReModels <-
%     bind_rows(
%       leaf_apply(resampleModelsCES, 
%                  function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
%                  strict.lists = TRUE)
%     )
% }
% @

@@

  ggplot() + 
  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
  facet_grid(flavor ~ Country) + 
  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
  xlab("") + 
  ylab("Indexed (1960=1)") +
  xy_theme() %>%
  graph_text_size_style(graph_text_size)
@

>>>>

resampleCoeffsCESFilename <- "EcolEcon2015kleResampleCoeffsCES.rds"
resampleModelsCESFilename <- "EcolEcon2015kleResampleModelsCES.rds"
ReModelsFilename <- "ReModels.rds"
if (rerunResampling){
  # Run some resampling on the PT and UK models that reject the cost-share theorem,
  # include energy, use quality-adjusted variables, and employ the (kl)e nesting.
  # This is u-g-l-y code. Just getting something running for now.
  modPT <- models$PT$adjusted$withE$CES$kle
  modUK <- models$UK$adjusted$withE$CES$kle
  resamplesCESPT <- resampledFits(modPT, method = "wild", n = nResamples)
  resamplesCESUK <- resampledFits(modUK, method = "wild", n = nResamples)
  # Resample model objects
  resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
  # Save this object in case we need to interrogate it later.
  # Note, however, that resampleModelsCES is NOT in the repository,
  # because it can be a HUGE file when we're doing, say, 1000 resamples.
  saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
  # Resample time series
  ReModels <-
    bind_rows(
      leaf_apply(resampleModelsCES, 
                 function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
                 strict.lists = TRUE)
    )
  saveRDS(ReModels, file = ReModelsFilename)
  # Resample coefficients
  resampleCoeffsCES <- bind_rows(
    bind_cols(resamplesCESPT$coeffs %>% mutate(Country="PT")), 
    bind_cols(resamplesCESUK$coeffs %>% mutate(Country="UK")))
  resampleCoeffsCES$energy <- TRUE
  resampleCoeffsCES$nest <- "(kl)e"
  saveRDS(resampleCoeffsCES, file = resampleCoeffsCESFilename)
} else {
  resampleCoeffsCES <- readRDS(resampleCoeffsCESFilename)
  # We don't need to load resampelModelsCES, because we use only ReModels later.
  # But, you can uncomment this line to load an archived file, if desired.
  # resampleModelsCES <- readRDS(resampleModelsCESFilename)
  ReModels <- readRDS(ReModelsFilename)
}
@

@@

  ggplot() + 
  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
  facet_grid(flavor ~ Country) + 
  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
  xlab(NULL) + 
  ylab("Indexed (1960=1)") +
  xy_theme() %>%
  graph_text_size_style(graph_text_size)
@

### 2016-07-21 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Add sd calc on delta_1.
"" --> NULL for xlab.

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.8, fig.cap="Historical cost shares for capital and labor.">>=
gather(CostShares, key=cost_share, value=value, cs_k, cs_l) %>%
  mutate(
    cost_share = relevelFactor(factor(cost_share), c("cs_l", "cs_k"))
  ) %>%
ggplot() + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share,
    size = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(0.0, 1.0), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab("") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("l", "k"),
                     values=c("black", "black")) +
  scale_linetype_manual(name="", 
                        labels=c("l", "k"),
                        values=c(3,2)) + 
  scale_size_manual(name="", 
                    labels=c("l", "k"),
                    values = c(0.9, 0.9)) +
  xy_theme() %>%
  graph_text_size_style(graph_text_size)
@

@@

  ggplot(aes(x = xlabels, weight = lambda)) + 
    facet_grid(Nest ~ Country) +
    geom_bar(fill = "white", colour = "black", width = 0.2) +
    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
    xlab("") +
    ylab(expression(lambda)) +
    xy_theme() + 
    theme(
      axis.text.x = element_text(angle = 90, hjust = 1),
      axis.ticks.x = element_blank()
    ) %>%
  graph_text_size_style(graph_text_size)
@

@@

<<PT-resample-quantiles, echo = TRUE, include = TRUE>>=
PTkleresample <- resampleCoeffsCES %>% filter(Country == "PT", method != "orig")
any(PTkleresample$delta_1 >= 1)
1 - max(PTkleresample$delta_1)
PTklerange95 <- quantile(PTkleresample$delta_1, probs=c(0.025, 0.975))
PTklerange95
1 - PTklerange95
# See if there are any coefficients that are exactly 0.5, the starting value.
any(resampleCoeffsCES$delta_1 == 0.5)
@

>>>>

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.8, fig.cap="Historical cost shares for capital and labor.">>=
gather(CostShares, key=cost_share, value=value, cs_k, cs_l) %>%
  mutate(
    cost_share = relevelFactor(factor(cost_share), c("cs_l", "cs_k"))
  ) %>%
ggplot() + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share,
    size = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(0.0, 1.0), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab(NULL) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("l", "k"),
                     values=c("black", "black")) +
  scale_linetype_manual(name="", 
                        labels=c("l", "k"),
                        values=c(3,2)) + 
  scale_size_manual(name="", 
                    labels=c("l", "k"),
                    values = c(0.9, 0.9)) +
  xy_theme() %>%
  graph_text_size_style(graph_text_size)
@

@@

  ggplot(aes(x = xlabels, weight = lambda)) + 
    facet_grid(Nest ~ Country) +
    geom_bar(fill = "white", colour = "black", width = 0.2) +
    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
    xlab(NULL) +
    ylab(expression(lambda)) +
    xy_theme() + 
    theme(
      axis.text.x = element_text(angle = 90, hjust = 1),
      axis.ticks.x = element_blank()
    ) %>%
  graph_text_size_style(graph_text_size)
@

@@

<<PT-resample-quantiles, echo = TRUE, include = TRUE>>=
PTkleresample <- resampleCoeffsCES %>% filter(Country == "PT", method != "orig")
any(PTkleresample$delta_1 >= 1)
1 - max(PTkleresample$delta_1)
PTklerange95 <- quantile(PTkleresample$delta_1, probs=c(0.025, 0.975))
PTklerange95
1 - PTklerange95
# See if there are any coefficients that are exactly 0.5, the starting value.
any(PTkleresample$delta_1 == 0.5)
# Calculate standard deviation of the delta_1 resampling distribution.
sd(PTkleresample$delta_1)
@
